**Preprinting Microbiology**

### 2017-01-12 submission/Schloss_PrePrints_mBio_2017.Rmd
Finish updating affiliation lookup table

```{r analysis}
biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv', header=T, sep='\t', stringsAsFactors=F)

@@

micro_aff_institutes <- levels(as.factor(biorxiv[micro_affiliated, "affiliation"]))
micro_aff_countries_count <- sort(table(lookup[biorxiv[micro_affiliated, "affiliation"], "country"]), decreasing=T)
micro_aff_countries_percent <- 100 * micro_aff_countries_count / sum(micro_aff_countries_count)
micro_aff_countries_names <- names(micro_aff_countries_percent)

@@

***Metrics for microbiology preprints.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016. We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts (**Figure 1**). These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r r non_micro_category_counts[3]`) categories. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories. Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints. Corresponding authors that have posted microbiology-affiliated preprints are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).

>>>>

```{r analysis}
biorxiv <- read.table(file = 'data/processed/biorxiv_data_summary.tsv', header=T, sep='\t', stringsAsFactors=F)
biorxiv$affiliation <- gsub(";\\s*$", "", biorxiv$affiliation)

@@

micro_aff_institutes <- levels(as.factor(biorxiv[micro_affiliated, "affiliation"]))

micro_aff_countries_count <- sort(table(lookup[biorxiv[micro_affiliated, "affiliation"], "country"]), decreasing=T)
micro_aff_countries_percent <- 100 * micro_aff_countries_count / sum(micro_aff_countries_count)
micro_aff_countries_names <- names(micro_aff_countries_percent)

@@

***Metrics for microbiology preprints.*** To analyze the use of preprints, we copied the bioRxiv website on December 31, 2016. We chose to analyze the use of *bioRxiv* preprints because these preprints are amenable for submission to ASM journals and there were `r nrow(biorxiv)` preprints compared to the 2,650 available at *PeerJ Preprint*. Among the `r nrow(biorxiv)` preprints on bioRxiv, `r sum(biorxiv$category=="Microbiology", na.rm=T)` were assigned by the authors into the Microbiology category. When we used a more permissive classification system to identify microbiology-affiliated preprints, we identified `r sum(non_micro_micro, na.rm=T)` additional manuscripts (**Figure 1**). These microbiology-affiliated preprints were primarily assigned to the `r non_micro_category_names[1]` (N=`r non_micro_category_counts[1]`), `r non_micro_category_names[2]` (N=`r non_micro_category_counts[2]`), or `r non_micro_category_names[3]` (N=`r r non_micro_category_counts[3]`) categories. One limitation of the *bioRxiv* interface is the inability to assign manuscripts to multiple categories or to tag the content of the preprint. For example, this manuscript could be assigned to either the Microbiology or Scientific Communication and Education categories. Reflecting the still relatively novelty of preprints, `r sum(micro_aff_author_counts == 1)` (`r 100*sum(micro_aff_author_counts == 1)/length(micro_aff_author_counts)`%) corresponding authors who submitted a microbiology-affiliated manuscript (N=`r length(micro_aff_author_counts)` total) have posted a single preprint and `r 100*sum(micro_aff_author_counts >= 3)/length(micro_aff_author_counts)`% have posted 3 or more preprints. Corresponding authors that have posted microbiology-affiliated preprints are from `r length(micro_aff_countries_names)` countries and are primarily affiliated with institutions in the `r micro_aff_countries_names[1]` (`r micro_aff_countries_percent[1]`% of microbiology-affiliated preprints), `r micro_aff_countries_names[2]` (`r micro_aff_countries_percent[2]`%), and `r micro_aff_countries_names[3]` (`r micro_aff_countries_percent[3]`%).
